Mapping mutational effects along the evolutionary landscape of HIV envelope

### 2017-12-15 paper/manuscript_Hugh.tex
Another minor tweak to Hugh's comments

\begin{figure}
{\bf \Large A} \\
\includegraphics[width=0.8\textwidth]{figures/shifts_on_structure/shifts_on_structure.pdf}
\\
{\bf \Large B} \hspace{0.28\textwidth} {\bf \Large C} \hspace{0.28\textwidth} {\bf \Large D} \\
\includegraphics[width=0.28\textwidth]{figures/rsa_vs_shifts.pdf}
\hspace{0.01\textwidth}
\includegraphics[width=0.28\textwidth]{figures/shifts_proximity.pdf}
\hspace{0.01\textwidth}
\includegraphics[width=0.4\textwidth]{figures/conservation_vs_shifts.pdf} 
\caption{\label{fig:shiftfeatures}
Characteristics of significantly shifted sites.
{\bf (A)} One monomer of the Env trimer~\citep[PDB 5FYL;][]{stewart2016trimeric} is colored from gray to orange according to the magnitude of the mutational shift at each site (orange indicates large shift).
Sites that are significantly shifted according to Figure~\ref{fig:prefsdist}B are in spheres, and all other sites are in cartoon representation.
{\bf (B)} 
There is no significant difference in the relative solvent accessibility of sites that have and have not undergone significant shifts.
The absolute solvent accessibility of each site was calculated using DSSP~\citep{kabsch1983dictionary} and normalized to a relative solvent accessibility using the absolute accessibilities from \citet{tien2013maximum}.
{\bf (C)} 
Sites of significant shifts are clustered in Env's structure.
Shown is the distance of each significantly shifted and not-shifted site to the closest other shifted site.
{\bf (D)}
Large mutational shifts are \emph{not} strongly enriched at sites that have substituted between BG505 and BF520, or at sites that contact sites that have substituted. 
The plot shows the magnitudes of the shifts among the 83 crystallographically resolved sites that have substituted between BG505 and BF520, the 234 sites that physically contact a substitution in the Env structure (any non-hydrogen atom within 3.5\angstrom), and all other sites.
\hhcomment{On a second reading of this figure, I'm a bit confused. It seems like sites that fall into the "substitution" category would also fall into either the "contacts substitution" or the "not near substitution" category. I'm not sure I understand the rationale for why the three categories would all be mutually exclusive. It seems to me like a more straightforward comparison would be for panel D to \emph{only} compare sites based on whether or not they contact a substituted site, i.e., removing the "substitution" box plot. Since the supplemental table to this figure already tests for a difference in shifted vs. non-shifted sites, it doesn't seem like removing the "substitution" box plot would leave us with much less information. I would be interested to hear your thoughts on this if you have time to talk over the phone or in person.}
Figure~\ref{fig:shiftfeatures}-Figure~supplement~\ref{figsupp:subs_shifts} shows that there is a modest borderline-significant tendency of significantly shifted sites to have substituted.
All panels only show the 577 sites that are resolved in the crystal structure.
Of the 30 significantly shifted sites in Figure~\ref{fig:prefsdist}B, only 28 are crystallographically resolved.
Structural distances and solvent accessibilities were calculated using all monomers in the trimer.
$P$ values were calculated using the Mann-Whitney $U$ test.
}
\figsupp[\label{figsupp:subs_shifts}Statistical testing of whether significantly shifted sites are more likely to have substituted between BG505 and BF520.]
{The sites of significant shifts as determined in Figure~\ref{fig:prefsdist}B are somewhat more likely to be among the sites that have substituted between BG505 and BF520.
However, this association is only borderline statistically significant, with $P = 0.055$ using a Fisher's exact test.}
{\input{figures/shifts_vs_subs_table}}
\end{figure}

>>>>

\begin{figure}
{\bf \Large A} \\
\includegraphics[width=0.8\textwidth]{figures/shifts_on_structure/shifts_on_structure.pdf}
\\
{\bf \Large B} \hspace{0.28\textwidth} {\bf \Large C} \hspace{0.28\textwidth} {\bf \Large D} \\
\includegraphics[width=0.28\textwidth]{figures/rsa_vs_shifts.pdf}
\hspace{0.01\textwidth}
\includegraphics[width=0.28\textwidth]{figures/shifts_proximity.pdf}
\hspace{0.01\textwidth}
\includegraphics[width=0.4\textwidth]{figures/conservation_vs_shifts.pdf} 
\caption{\label{fig:shiftfeatures}
Characteristics of significantly shifted sites.
{\bf (A)} One monomer of the Env trimer~\citep[PDB 5FYL;][]{stewart2016trimeric} is colored from gray to orange according to the magnitude of the mutational shift at each site (orange indicates large shift).
Sites that are significantly shifted according to Figure~\ref{fig:prefsdist}B are in spheres, and all other sites are in cartoon representation.
{\bf (B)} 
There is no significant difference in the relative solvent accessibility of sites that have and have not undergone significant shifts.
The absolute solvent accessibility of each site was calculated using DSSP~\citep{kabsch1983dictionary} and normalized to a relative solvent accessibility using the absolute accessibilities from \citet{tien2013maximum}.
{\bf (C)} 
Sites of significant shifts are clustered in Env's structure.
Shown is the distance of each significantly shifted and not-shifted site to the closest other shifted site.
{\bf (D)}
Large mutational shifts are \emph{not} strongly enriched at sites that have substituted between BG505 and BF520, or at sites that contact sites that have substituted. 
The plot shows the magnitudes of the shifts among the 83 crystallographically resolved sites that have substituted between BG505 and BF520, the 234 sites that physically contact a substitution in the Env structure (any non-hydrogen atom within 3.5\angstrom), and all other sites.
\hhcomment{On a second reading of this figure, I'm a bit confused. It seems like sites that fall into the "substitution" category would also fall into either the "contacts substitution" or the "not near substitution" category. I'm not sure I understand the rationale for why the three categories would all be mutually exclusive. It seems to me like a more straightforward comparison would be for panel D to \emph{only} compare sites based on whether or not they contact a substituted site, i.e., removing the "substitution" box plot. Since the supplemental table to this figure already tests for a difference in shifts at substituted vs. non-substituted sites, it doesn't seem like removing the "substitution" box plot would leave us with much less information. I would be interested to hear your thoughts on this if you have time to talk over the phone or in person.}
Figure~\ref{fig:shiftfeatures}-Figure~supplement~\ref{figsupp:subs_shifts} shows that there is a modest borderline-significant tendency of significantly shifted sites to have substituted.
All panels only show the 577 sites that are resolved in the crystal structure.
Of the 30 significantly shifted sites in Figure~\ref{fig:prefsdist}B, only 28 are crystallographically resolved.
Structural distances and solvent accessibilities were calculated using all monomers in the trimer.
$P$ values were calculated using the Mann-Whitney $U$ test.
}
\figsupp[\label{figsupp:subs_shifts}Statistical testing of whether significantly shifted sites are more likely to have substituted between BG505 and BF520.]
{The sites of significant shifts as determined in Figure~\ref{fig:prefsdist}B are somewhat more likely to be among the sites that have substituted between BG505 and BF520.
However, this association is only borderline statistically significant, with $P = 0.055$ using a Fisher's exact test.}
{\input{figures/shifts_vs_subs_table}}
\end{figure}
